
```{r solutions, echo=FALSE}
# This is optional to prevent annoying errors when deploying shiny apps
if(!exists(".flexteach_solutions"))
  .flexteach_solutions = FALSE
```

```{r, setup}
## See https://bookdown.org/yihui/rmarkdown-cookbook/rgl-3d.html
library(rgl)
knitr::knit_hooks$set(webgl = hook_webgl)
```

This demo assignment demonstrates the loading of a page in an `iframe` using the `srcdoc` attribute, so that the assignment is rendered as a complete webpage. This allows things like `htmlwidgets` to be run in the page without using extra javascript (just as it would be rendered locally).

This has several slight downsides:

* The pages are rendered somewhat slower and are larger, because a full webpage is rendered instead of a fragment
* The assignment is isolated from the rest of the app; so, for instance, buttons cannot be moved from inside the assignment to the top button bar.

If you want interactive javascript apps without these downsides, you'd need to work out what javascript should run when the page loads and run it using the `on-load` yaml option for the assignment (see the [wiki](https://github.com/richarddmorey/flexTeaching/wiki/Creating-assignments)).

The key to making this assignment work is rendering the page with the `compileAssignmentHtml_iframe()` function in `R/utility.R`.

## Test some `htmlwidgets`

### DiagrammeR

See https://rich-iannone.github.io/DiagrammeR/

```{r echo=FALSE}
DiagrammeR::grViz("flexTeach.gv", height=400)
```

### rgl

See https://bookdown.org/yihui/rmarkdown-cookbook/rgl-3d.html.

```{r, test-rgl, webgl=TRUE}
x <- sort(rnorm(1000))
y <- rnorm(1000)
z <- rnorm(1000) + atan2(x,y)
plot3d(x, y, z, col = rainbow(1000))
```

### graph3d

See https://github.com/stla/graph3d

```{r echo=FALSE}
# bivariate Gaussian density ####
dat <- expand.grid(
x = seq(-4,4,length.out=100),
y = seq(-4,4,length.out=100)
)
dat <- transform(dat, density = dnorm(x)*dnorm(y))
graph3d::graph3d(dat, z = ~density, keepAspectRatio = FALSE, verticalRatio = 1)
```

### sigmaNet

See https://iankloo.github.io/sigmaNet/

```{r echo=FALSE, message=FALSE}
library(sigmaNet)
library(igraph)

data(lesMis)

clust <- cluster_edge_betweenness(lesMis)$membership
V(lesMis)$group <- clust

layout <- layout_with_fr(lesMis)

sig <- sigmaFromIgraph(lesMis, layout = layout) %>%
  addNodeLabels(labelAttr = 'label') %>%
  addEdgeSize(sizeAttr = 'value', minSize = .1, maxSize = 2) %>%
  addNodeSize(sizeMetric = 'degree', minSize = 2, maxSize = 8) %>%
  addNodeColors(colorAttr = 'group', colorPal = 'Set1')
sig
```
